---
title: "314 A1-vignette"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE, warning=FALSE}
library(imager)
library(tidyverse)
library(tidymodels)
library(dplyr)
library(sp)
library(scales)
library(cowplot)
library(ggplot2)
#install.packages("devtools")
#library(devtools)
#devtools::install_github("sharlagelfand/dmc")
library(dmc)

source('functions.R')
```
The tasks for this project is to write several R functions that will take an image and create a cross-stitch pattern. I write the function in 'function.R', and I will test the function in following parts.

First, I load the image by function imager::load.image(). The following is the picture I use.
```{r}
set.seed(8477)
image_file_name<-'Crayon.jpg'
im<-imager::load.image(image_file_name)
plot(im,main="Image")
```

The second step is to gain the tibble of information derived from the k_means. We use the function process_image() and store the result in 'gain_clusters'. Each row provide information for k-means clustering of each k.

k: k value from 2-8

totss: The total sum of squares.

betweenss: The between-cluster sum of squares, i.e. $totss-tot.withinss$.

tot.withinss: Total within-cluster sum of squares, i.e. sum(withinss).

totss, tot.withinss, betweenss, and iter (1 value) contain information about the full clustering

centers(nested column): A matrix of cluster centers.
tidy_dat: contains coordinate,RGB information abour original data points.
centers and tidy_dat contain information about each cluster
```{r message=FALSE, warning=FALSE}
gain_clusters<-process_image(image_file_name,k=2:8)
gain_clusters
```

The third step is to produce and plot a scree plot. We use the function scree_plot() and recieve one graph with two plots.

The within-cluster sum of squares used to measure the variability of the observations within each cluster

The left graph shows that the total within-cluster sum of squares is decreasing slowly after k=4. After k=5,the total within-cluster sum of squares is close to the results in k=5. The value at k=5 is good.

The right graph shows the change of ratio(=tot.withinss(k)/tot.withinss(k-1)). 

When k=7,ratio=tot.withinss(7)/tot.withinss(6)=0.74. The tot.withinss(k=7) is 72% of tot.withinss(k=6).

When k=6,ratio=tot.withinss(6)/tot.withinss(5)=0.72. The tot.withinss(k=6) is 72% of tot.withinss(k=5).

When k=5,ratio=tot.withinss(5)/tot.withinss(4)=0.22. The tot.withinss(k=5) is 22% of tot.withinss(k=4). 

From this the number of clusters seems to be 6 or 7 (because increase trend becomes slow). And the tot.withinss is close when k=5,6 and 7. So we cannot have a certain conclusion that 6 is the right number of clusters. We will check it in following colour_strips.
```{r}
scree_plot(gain_clusters)
```

We use function colour_strips() to produce colour strips with the DMC colour.
Visually,when k=6, color black and color dark blue is too similar (dark tones) . 
Let’s see what happens if we choose k-5, 5 colors are clearly unlike each other. So K=5 is much better choice.
```{r}
colour_strips(gain_clusters)
```
So now we have 5 clusters we need to put it into make_pattern() function, and produce a cross stitch pattern that can be followed.
I graph 2 versions, one with color and one without color.
```{r}
#Pattern with Colour & Background
make_pattern(cluster_info=gain_clusters, k=5, x_size=90, 
             black_white =FALSE,background_colour=NULL)+
  ggtitle("Pattern with Colour & Background")+
  background_grid(color.major = "black",color.minor = "black")
```


```{r}
#Pattern with Background & no color
make_pattern(cluster_info=gain_clusters, k=5, x_size=50, 
             black_white =TRUE,background_colour=NULL)+
  ggtitle("Pattern with Colour & Background")+
  background_grid(color.major = "black",color.minor = "black")
```


